---
title: "Analysis of 1000 Cameras"
author: "Bilge Uzuner - BDA 503 - Fall 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### ABOUT DATA

Some camera enthusiast described 1,000 cameras based on 13 properties, such as weight, focal length, price, etc. Data includes the records of 1038 camera models of 21 different brands. 

These datasets have been gathered and cleaned up by Petra Isenberg, Pierre Dragicevic and Yvonne Jansen. The original source can be found [here](/perso.telecom-paristech.fr/eagan/class/igr204/datasets)

Row one describes the datatype for each column and can probably be removed.

## The 13 properties of each camera:

* **Model**
* **Release date** The Date From Which the product is On Sale
* **Max resolution** highest dimension in pixel 
* **Low resolution** lowest dimensions in pixel
* **Effective pixels** Effective pixels are the pixels that are actually capturing the image data. They are effective and by definition, effective means "successful in producing a desired effect or intended result." These are the pixels that are doing the work of capturing a picture.
* **Zoom wide (*W*)** 
* **Zoom tele (*T*)** zoom wide and zoom tele are the two important figures that shows focal lengths
* **Normal focus range** distance which focus can be obtained
* **Macro focus range** It's the nearest distance between the camera and the subject such that the camera can take clear and in-focus shots
* **Storage included** Local camera storage included
* **Weight (*inc.batteries*)** weight of the camera including bateries
* **Dimensions** Length and width of the camera
* **Price** 

******

### Initial Exploratory Analysis

```{r,echo=FALSE,results="hide",include=FALSE}

library(readr)
camera_dataset <- read_csv("D:/Users/buzuner/Downloads/camera_dataset.csv")
```


```{r,echo=FALSE,results="hide",include=FALSE}
# Summary of 1000 cameras
str(camera_dataset)


library(dplyr)#glimpse function
```



```{r}
#Nature of rows and columns//quick review of dataset
glimpse(camera_dataset)

#Number of rows and columns
dim(camera_dataset)
```



```{r,echo=FALSE,results="hide",include=FALSE}
# output:
# Camera Models: 1,038
# Variables: 13


mean(camera_dataset$Price)
```



```{r}
# Which camera has the maximum price?

max(camera_dataset$Price)

```


  
#### References

Dataset;

[https://www.kaggle.com/plarmuseau/camera-notes/data](https://www.kaggle.com/plarmuseau/camera-notes/data)

Analysis;

[https://cran.r-project.org/doc/contrib/Paradis-rdebuts_en.pdf](https://cran.r-project.org/doc/contrib/Paradis-rdebuts_en.pdf)

[https://www.datacamp.com/courses/reporting-with-r-markdown](https://www.datacamp.com/courses/reporting-with-r-markdown)

[https://www.rstudio.com/resources/cheatsheets/](https://www.rstudio.com/resources/cheatsheets/)
































































































































































































































































































